Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-12 main.tex
Update to the abstract

% Abstract of not more than 200 words.
\begin{abstract}
Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy. Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common, model-based, non-linear measurement, localisation methods and forfeit broad applicability. We define a cryptographically secure linear-combination aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation. The security requirements, leakage, and cryptographic proof are given for the private filter and aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method. Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
\end{abstract}

>>>>

% Abstract of not more than 200 words.
\begin{abstract}
Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localisation protocols, thus not preserving participants’ data privacy. Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common non-linear measurement model applications and forfeit broad applicability. We define the novel notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Information Filter with range-sensor measurements. Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and is implemented and run on simulations to evaluate its accuracy and performance. The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where nodes are not trusted or data is considered sensitive.
\end{abstract}
